### 2019-09-06 manuscript/manuscript.tex
G's changes mostly to intro

A long-standing problem in evolutionary genetics is quantifying the roles drift
and selection have in shaping genome-wide allele frequency changes. Previous
work on this question has focused on teasing apart the impacts of drift and
selection on genome-wide diversity using population samples from a single
contemporary timepoint, usually by modeling the correlation between regional
recombination rate and diversity created in the presence of linked selection
\parencite{Begun1992-ey,Elyashiv2016-vt}. While this approach has dramatically
informed our present view of the role of linked selection in shaping patterns
of genome-wide diversity across a variety of organisms
\parencite{Begun2007-bg,Beissinger2016-cm,Sattath2011-dr,Williamson2014-oy,Andersen2012-bj,Cutter2010-gi},
and has allowed us to quantity the relative roles positive selection
(hitchhiking) and negative selection (background selection) have shaping
patterns of genome-wide diversity
\parencite{Nordborg2005-dc,McVicker2009-ax,Hernandez2011-gs,Elyashiv2016-vt},
we fully lack an understanding of how linked selection acts over an important
dimension: time.

Presently, there are numerous examples of phenotypes rapidly evolving
\parencite{Grant2011-wk,Grant2006-hj,Reznick1997-mh,Franks2007-dr} yet the
polygenic nature of fitness makes detecting the impact selection has on
genome-wide variation over short timescales remarkably difficult. This is
because the effect of selection on a polygenic trait (such as fitness) is
distributed across loci proportional to their effect sizes, leading to subtle
allele frequency shifts that are difficult to distinguish from background
levels of genetic drift and sampling variance. However, increasingly genomic
studies with multiple timepoints and, in some cases, multiple replicate
populations are becoming available, are being used to detect selected loci
\parencite{Turner2011-sx,Turner2012-bm} and differentiate modes of selection
\parencite{Burke2010-tz,Barghi2019-qy}. In a previous paper, we proposed that
one signal of polygenic linked selection that could be detected from these
temporal genomic studies is the temporal autocovariance in allele frequency
changes \parencite{Buffalo2019-io}. These covariances are directly estimable
from temporal genomic data and are created when the loci that underly heritable
fitness variation perturbed linked neutral alleles; when genetic drift acts
alone in a closed population, these covariances are zero in expectation.

>>>>

A long-standing problem in evolutionary genetics is quantifying the
roles \gc{genetic} drift
and selection have in shaping genome-wide allele frequency
changes. Seletion can both directly and indirectly affect
allele frequency change, with the indirect effect coming from the
action of selection on \gc{correlated loci elsewhere in genome
  e.g. linked selection \parencite{MaynardSmith,Charleseworths,etc}}.
Previous
work on this question has \gc{mostly} focused on teasing apart the impacts of drift and
selection on genome-wide diversity using population samples from a single
contemporary timepoint, \gc{often} by modeling the correlation between regional
recombination rate, \gc{gene density,} and diversity created in the presence of linked selection
\parencite{Begun1992-ey,Elyashiv2016-vt}. \gc{This} approach has
\gc{shown a major }
role \gc{for} linked selection in shaping patterns
of genome-wide diversity across \gc{the gneomes of} a variety of organisms
\parencite{Begun2007-bg,Beissinger2016-cm,Sattath2011-dr,Williamson2014-oy,Andersen2012-bj,Cutter2010-gi},
and has allowed us to quantity the relative roles positive selection
(hitchhiking) and negative selection (background selection) have shaping
patterns of genome-wide diversity
\parencite{Nordborg2005-dc,McVicker2009-ax,Hernandez2011-gs,Elyashiv2016-vt}.
\gc{However, we} lack an understanding of how \gc{genome-wide} linked selection acts over an important
dimension: time.

Presently, there are numerous examples of \gc{rapid phenotypic adaptation}
\parencite{Grant2011-wk,Grant2006-hj,Reznick1997-mh,Franks2007-dr}
and \gc{rapid genomic evolution in asexual populations \parencite{Lenski,Desai}.}
Yet the
polygenic nature of fitness makes detecting the impact selection has on
genome-wide variation over short timescales \gc{in sexual populations} remarkably difficult. This is
because the effect of selection on a polygenic trait (such as fitness) is
distributed across loci proportional to their effect sizes, \gc{which
  can} lead to subtle  %want to be careful here as Kevin T and
                       %Wolfgang would say that
allele frequency shifts that are difficult to distinguish from background
levels of genetic drift and sampling variance. However, increasingly genomic
\gc{experimental evolution} studies with multiple timepoints and, in some cases, multiple replicate
populations are becoming available, are being used to detect selected loci
\parencite{Turner2011-sx,Turner2012-bm} and differentiate modes of
selection %cite silver fish by Nina and others
\parencite{Burke2010-tz,Barghi2019-qy}. \gc{In addition these temporal-genomic
  studies have begun in wild populations \parencite{Bergland,Machado,Othere}
 } In a previous paper, we proposed that
one signal of polygenic linked selection that could be detected from these
temporal genomic studies is the temporal autocovariance in allele frequency
changes \parencite{Buffalo2019-io}. These covariances are directly estimable
from temporal genomic data and are created when the loci that underly heritable
fitness variation perturbed linked neutral alleles; when genetic drift acts
alone in a closed population, these covariances are zero in expectation.
\gc{The covariances provide a useful tool for understanding the
  gneome-wide imapct of linked selection. First, because it is
  mathematically natural
  to decompose the total variance in temporal allele frequency change
  across a set of time intervals into the covariances in allele
  frequency change among time intervals. Second, because biologically
  the covariances reflect the correlation of selection coefficients
  experienced in different time intervals. }
